---
title: "Fibonacci Plot"
author: "Richard Kriz"
date: "13.03.2019"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pressure, echo=FALSE}
data <- read.csv(file="/home/richard/owncloud/BINF/AlgoUE2019/A1/time_outputs.csv", header = TRUE, sep = ",")
plot(data$iteration, data$time_.s., ylab="time (s)", xlab = "Iteration")
points(data$iteration[data$algorithm == "linear"],
       data$time_.s.[data$algorithm == "linear"], col =
         "black", pch = 19)
points(data$iteration[data$algorithm == "exp_index"],
       data$time_.s.[data$algorithm == "exp_index"], col =
         "red", pch = 19)
points(data$iteration[data$algorithm == "exp_max()_iter"],
       data$time_.s.[data$algorithm == "exp_max()_iter"], col =
         "green", pch = 19)
legend("topleft", pch = 19, col = c("black", "red", "green"), c("linear", "exp_index", "exp_max()_iter"))
```

## Linear: linear, efficient algorithm
## exp_index: exponential, inefficient algorithm, the efficient fibonacci algorithm is used as index for the returned values of the recursive functions
## exp_max()_iter: exponential, inefficient algorithm, each returned value is checked against the list of found fibonacci numbers, if it is higher than max, it is a new fibonacci number